On the Synchronization Power of OpenFlow

### 2015-03-06 inband-STN.tex
intro update, reorganised the content a bit

Even more, we observe that the standard also assumes \emph{conditional} application of
certain types of control messages. A specific $\textsf{OFPFF}\_\textsf{CHECK}\_\textsf{OVERLAP}$ flag
set in the control message containing a new forwarding rule ensures
that the rule is applied if and only if it does not \emph{conflict}
with any other rule currently in the flow table.  
This in-band conflict detection mechanism, combined with bundling,
allows us to implement specific types of \emph{transactions} that may
atomically install multiple rules if certain compatibility conditions
are met.

@@

@@

%\paragraph{Organization.}
%
The rest of the paper is organized as follows.
In Section~\ref{sec:background}, we provide the theoretical
background on our approach. Section~\ref{sec:realization}
then discusses the basic implementation of this approach in Openflow.
Section~\ref{sec:extensions} discusses practical issues and extensions.
After reviewing related literature in Section~\ref{sec:relwork},
we conclude our work in
Section~\ref{sec:conclusion}.

@@

\section{Improving the scheme with advanced OpenFlow features}\label{sec:todo}
Till now we considered a model that allows multiple updates to match-action entries. Here we extends the model with actions create-entry and delete-entry that may failed and abort the whole transaction depending on the existence on non-existence of specific entries prior to the action.
%TBD - much less resources. easily solving the infinite versions issue.

\section{Solving just concurrent policy update without consensus}\label{sec:todo}

TBD - should be simple given two previous sections

>>>>

Even more, we observe that the standard also assumes \emph{conditional} application of
certain types of control messages. A specific $\textsf{OFPFF\_CHECK\_OVERLAP}$ flag
set in the control message containing a new forwarding rule ensures
that the rule is applied if and only if it does not \emph{conflict}
with any other rule currently in the flow table.  
This in-band conflict detection mechanism, combined with bundling,
allows us to implement specific types of \emph{transactions} that may
atomically install multiple rules if certain compatibility conditions
are met.

@@

Our results highlight the surprising synchronization power hidden in the
OpenFlow standard. The synchronization mechanisms we describe in this
paper turn out to be crucial for ensuring consistency of network
management on the control plane while preserving consistency of the
traffic processed on the data plane.

@@

%\paragraph{Organization.}
%
The rest of the paper is organized as follows.
In Section~\ref{sec:model}, we overview the basics of the  OpenFlow
protocol and recall the bundle and \textsf{ofpff\_check\_overlap} features. 
In Section~\ref{sec:sync}, we specify the implementations of our OpenFlow-based
sycnhronization mechanisms. 
In Section~\ref{sec:application}, we discuss a few policy composition
algorithms that benefit from these mechanisms. 
In Section~\ref{sec:conclusion}, we discuss open questions and related work.

%we provide the theoretical
%background on our approach. Section~\ref{sec:realization}
%then discusses the basic implementation of this approach in Openflow.
%Section~\ref{sec:extensions} discusses practical issues and extensions.
%After reviewing related literature in Section~\ref{sec:relwork},
%we conclude our work in
%Section~\ref{sec:conclusion}.

\section{SDN primer and OpenFlow features}\label{sec:model}

Define the protocol (from Reclaiming the Brain"?) and discuss bundling
and check-overlap.

\section{Transactions in OpenFlow}\label{sec:sync}

Multi-write and read-modify transactions.

\subsection{Improving the scheme with check-overlap}\label{sec:todo}
Till now we considered a model that allows multiple updates to match-action entries. Here we extends the model with actions create-entry and delete-entry that may failed and abort the whole transaction depending on the existence on non-existence of specific entries prior to the action.
%TBD - much less resources. easily solving the infinite versions issue.

\section{Applications and ramifications}\label{sec:application}

@@
